%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass[10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here
\usepackage[hidelinks]{hyperref}
\usepackage{tgpagella}
\usepackage[sf,scale=0.95]{libertine}
\usepackage{helvet} % Default font is the helvetica postscript font
\usepackage{url}
\urlstyle{rm}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage[usenames,dvipsnames]{color}
\usepackage{wasysym}
\usepackage{marvosym}
\usepackage{xfakebold}
%\usepackage[margin=0.5in]{geometry}
\usepackage[left=1.2cm, right=1.2cm, top=1.5cm, bottom = 1.5cm]{geometry}
\usepackage[utf8]{inputenc}
\pagenumbering{arabic}
\newsectionwidth{0pt} % Stops section indenting
\setlength{\textwidth}{7.5in}
\setlength{\textheight}{9.8in}



\begin{document}


%----------------------------------------------------------------------------------------
%	YOUR NAME AND ADDRESS(ES) SECTION
%----------------------------------------------------------------------------------------

\name{\huge{{Brato Chakrabarti}}\\ \\} % Your name at the top
\address{\bf Assistant Professor\\ International Center for Theoretical Sciences \\ Tata Institute of Fundamental Research \\Bengaluru, India \\
\emph{Web:} \url{https://www.bratochakrabarti.com/} } % Your address 1


\address{{\bf Mailing address} \\ Survey No. 151, Shivakote,  \\ Hesaraghatta Hobli, Bengaluru  560089 \\ \phone \ (+91) 6291002341 \\ 
 \Letter \ {brato.chakrabarti@icts.res.in}   }% Your address 2

%----------------------------------------------------------------------------------------

\begin{resume}
\vspace*{-2mm}
\section{\color{Mahogany}{\large{RESEARCH INTERESTS}}}
\hrule
\hrule
\vspace*{4mm} % Gap between title and text
\begin{multicols}{3}
	\begin{itemize}
		\item[] Fluid dynamics
		\item[] Soft-matter physics
		\item[] Active matter
		\item[] Fluid-structure interaction
		\item[] Scientific computing
		\item[] Biological transport
		\item[] Biophysics
		\item[] Slender structures
		\item[] Mathematical modeling
	\end{itemize}
\end{multicols}

\vspace*{-4mm}
\section{\color{Mahogany}{\large{EMPLOYMENT}}}
\hrule
\hrule

\vspace*{4mm} % Gap between title and text
{\sl Reader} \hfill March 2024-Present \\
International Center for Theoretical Sciences \\ 
Tata Institute of Fundamental Research \\
Bengaluru, India 

\vspace*{4mm} % Gap between title and text
{\sl Flatiron Research Fellow} \hfill March 2020-January 2024 \\
Center for Computational Biology (CCB)  \\
Flatiron Institute, Simons Foundation  \\
Mentor: Professor Michael J. Shelley 


 
\vspace*{-2mm}
\section{\color{Mahogany}{\large{EDUCATION}}}
\hrule
\hrule

\vspace*{4mm} % Gap between title and text
{\sl Doctor of Philosophy}, 
Applied Mechanics   \hfill Fall 2015-Fall 2019 \\ 
Department of Mechanical and Aerospace Engineering (MAE) \\ 
University of California, San Diego \\
\textit{Thesis: Problems on Viscous Dynamics of Passive and Active Microfilaments} \\
Advisor: Professor David Saintillan 

 
{\sl Master of Science}, Engineering Mechanics \hfill Fall 2013-Spring 2015 \\
Biomedical Engineering and Mechanics \\ 
Virginia Tech \\
\textit{Thesis: Catenaries in Viscous Fluid} \\
Advisor: Professor James Hanna 


{\sl Bachelor of Engineering}, Mechanical Engineering \hfill 2009-2013 \\
Jadavpur University, India 

\vspace*{-3mm}


%---------------------------------------------------------------------------------------
\noindent\rule{\textwidth}{0.6pt}
\vspace*{-10mm}
\section{\color{Mahogany}{\large{PUBLICATIONS} \small{($^*$ denotes equal contribution)} }}
\vspace*{7mm} % Gap between title and text
\begin{enumerate}[topsep=0pt,itemsep= 1ex]
	
\item  Olenka Jain, \textbf{Brato Chakrabarti}, Reza Farhadifar, Elizabeth R. Gavis, Michael J. Shelley, and Stanislav Y. Shvartsman ``Geometric Effects in Large Scale Intracellular Flows", \href{https://doi.org/10.48550/arXiv.2409.06763}{arXiv:2409.06763}, (To appear in \textit{PRX Life}) (2025). 

	
\item  \textbf{Brato Chakrabarti}, Manas Rachh, SY Shvartsman, and  Michael J. Shelley ``Cytoplasmic stirring by active carpets",  \href{https://doi.org/10.1073/pnas.2405114121}{\textit{Proceedings of the National Academy of Sciences}},  \textbf{121} (2024).
	
\item Chenji Li, \textbf{Brato Chakrabarti}, Pedro Castilla, Achal Mahajan, and David Saintillan, ``Chemomechanical model of sperm locomotion reveals two modes of swimming
", \href{https://doi.org/10.1103/PhysRevFluids.8.113102}{\textit{Physical Review Fluids}}, \textbf{8} 113102 (2023). 
	
\item  \textbf{Brato Chakrabarti}, Michael J. Shelley, and  Sebastian F\"{u}rthauer ``Collective Motion and Pattern Formation in Phase-Synchronizing Active Fluids", \href{https://doi.org/10.1103/PhysRevLett.130.128202}{\textit{Physical Review Letters}} \textbf{130}, 128202 (2023).

\item Francesco Bonacci, \textbf{Brato Chakrabarti}, David Saintillan, Olivia du Roure, and Anke Lindner ``Dynamics of semiflexible polymers in oscillatory shear flows ", \href{https://doi.org/10.1017/jfm.2022.1040}{\textit{Journal of Fluid Mechanics}},  \textbf{955} A35 (2023).

\item  A. C. Quillen, A. Peshkov, \textbf{Brato Chakrabarti}, Nathan Skerrett, Sonia McGaffigan, and Rebeca Zapiach “Fluid circulation driven by collectively organized metachronal waves in swimming T. aceiti nematodes'',  \href{https://doi.org/10.1103/PhysRevE.106.06440}{\textit{Physical Review E}}, \textbf{106} 064401 (2022).  

\item \textbf{Brato Chakabarti}, Sebastian F\"{u}rthauer and Michael J. Shelley, ``A multiscale biophysical model gives quantized metachronal waves in a lattice of cilia",   \href{https://doi.org/10.1073/pnas.2113539119}{\textit{Proceedings of the National Academy of Sciences of the USA}} \textbf{119} (2022). 

\item \textbf{Brato Chakabarti}, Yanan Liu, Olivia du Roure, Anke Lindner, and David Saintillan, ``Signatures of elastoviscous buckling in the dilute rheology of stiff polymers",  \href{https://doi.org/10.1017/jfm.2021.383}{\textit{Journal of Fluid Mechanics}},  \textbf{919} A12 (2021).

\item \textbf{Brato Chakrabarti}, and David Saintillan, ``Shear-induced dispersion in peristaltic flow", \href{https://doi.org/10.1063/5.0030569}{\textit{Physics of Fluids}}, \textbf{32} 11302 (2020).  \textbf{Invited:} ``Contributions from Early Career Researchers 2020" and selected as a \textbf{featured} article.

\item \textbf{Brato Chakrabarti}, Charles Gaillard, and David Saintillan, ``Trapping, gliding, vaulting: Transport of semiflexible polymers in periodic post arrays", \href{DOI	https://doi.org/10.1039/D0SM00390E}{\textit{Soft Matter}}, \textbf{16} 5534 (2020).


\item \textbf{Brato Chakrabarti}, Yanan Liu, John Lagrone, Ricardo Cortez, Lisa Fauci, Olivia du Roure, David Saintillan, and Anke Lindner, ``Flexible filaments buckle into helicoidal shapes in strong compressional flow'',  \href{https://doi.org/10.1038/s41567-020-0843-7}{\textit{Nature Physics}}, (2020).

\item \textbf{Brato Chakrabarti} and David Saintillan, ``Hydrodynamic synchronization of spontaneously beating filaments'', \href{https://doi.org/10.1103/PhysRevLett.123.208101}{\textit{Physical Review Letters}}, \textbf{123} 208101 (2019). 


\item \textbf{Brato Chakrabarti} and David Saintillan, ``Spontaneous oscillations, beating patterns and hydrodynamics of active filaments", \href{https://doi.org/10.1103/PhysRevFluids.4.043102}{\textit{Physical Review Fluids}}, \textbf{4} 043102 (2019). 


\item Roberto Alonso Matilla, \textbf{Brato Chakrabarti} and David Saintillan, ``Transport and dispersion of active particles in periodic porous media", \href{https://doi.org/10.1103/PhysRevFluids.4.043101}{\textit{Physical Review Fluids}}, \textbf{4} 043101 (2019). 

\item Yanan Liu$^*$, \textbf{Brato Chakrabarti}$^*$, David Saintillan, Anke Lindner and Olivia du Roure, ``Tumbling, buckling, snaking: Morphological transitions
of flexible filaments in shear flow", \href{https://doi.org/10.1073/pnas.1805399115}{\textit{Proceedings of the National Academy of Sciences of the USA}}, \textbf{115} 9438 (2018).


\item \textbf{Brato Chakrabarti} and James Hanna ``Catenaries in Viscous Fluid", \href{https://doi.org/10.1016/j.jfluidstructs.2016.04.009}{\textit{Journal of Fluids and Structure}}, \textbf{66} 490–516 (2016).
\end{enumerate}


\vspace*{-2mm}
\noindent\rule{\textwidth}{0.6pt}
\vspace*{-10mm}
\section{\color{Mahogany}{\large{CONFERENCE ARTICLES AND PRESENTATIONS}  \small{(presenter underlined)}}} 
\vspace*{8mm}
\begin{enumerate}
\item  {Francesco Bonacci}, Brato Chakrabarti, Olivia du Roure, Anke Lindner, and \underline{David Saintillan}, \textit{Reversible to chaotic transitions in the dynamics of fluctuating elastic filaments in oscillatory shear flow}, at the 77th Annual Meeting of the APS Division of Fluid Dynamics, November 2024, Salt Lake City, USA.
	
\item  \underline{Brato Chakabarti}, and Michael J Shelley, \textit{A coarse-grained model for cytoplasmic streaming}, at the 76th Annual Meeting of the APS Division of Fluid Dynamics, November 2023, Washington DC, USA.

\item  \underline{Brato Chakabarti}, and Michael J Shelley, \textit{A coarse-grained model for cytoplasmic streaming}, at the APS March Meeting, 2023, Las Vegas, USA.

\item  \underline{Brato Chakabarti}, Sebastian F\"{u}rthauer and Michael J Shelley, \textit{Self-organized flows in phase-synchronizing active fluids}, at the APS March Meeting, 2022, Chicago, USA.
	
\item  \underline{Brato Chakabarti}, Sebastian F\"{u}rthauer and Michael J Shelley, \textit{A multiscale biophysical model gives quantized metachronal waves in a lattice of cilia}, at the APS March Meeting, 2022, Chicago, USA.
	
\item \underline{Francesco Bonacci}, Brato Chakrabarti, Olivia du Roure, Anke Lindner, and David Saintillan, \textit{Dynamics of semiflexible filaments in oscillatory shear flows}, at the Annual European Rheology Conference, Sevilla, 2022.

\item  \underline{Brato Chakabarti}, Sebastian F\"{u}rthauer and Michael J Shelley, \textit{A multiscale biophysical model gives quantized metachronal waves in a lattice of cilia}, at the 74th Annual Meeting of the APS Division of Fluid Dynamics, November 2021, Phoenix, USA.

\item \underline{David Saintillan}, Chenji Li, Brato Chakrabarti, Pedro Castilla, and Achal Mahajan \textit{An integrated chemomechanical model of sperm locomotion reveals two fundamental swimming modes}, at the 74th Annual Meeting of the APS Division of Fluid Dynamics, November 2021, Phoenix, USA.

\item \underline{David Saintillan}, Yanan Liu, John Lagrone, Ricardo Cortez, Lisa Fauci, Olivia du Roure, Anke Lindner, and Brato Chakrabarti \textit{Viscous dynamics of elastic filaments: from buckling instabilities to rheology},  at the APS March Meeting,  2021 (online).


\item \underline{Brato Chakabarti}, Yanan Liu, Olivia du Roure, Anke Lindner, and David Saintillan, \textit{Signatures of elastoviscous buckling in the dilute rheology of stiff polymers}, at the 73rd Annual Meeting of the APS Division of Fluid Dynamics, November 2020 (online).

\item \underline{David Saintillan}, and Brato Chakrabarti, \textit{Hydrodynamic synchronization of spontaneously beating filaments}, at the 72nd Annual Meeting of the APS Division of Fluid Dynamics, November 2019, Seattle, USA.

\item \underline{Brato Chakrabarti}, Yanan Liu, John Lagrone, Ricardo Cortez, Lisa Fauci, Olivia du Roure, David Saintillan, and Anke Lindner \textit{Helical buckling of flexible filaments in viscous flow},  at the 72nd Annual Meeting of the APS Division of Fluid Dynamics, November 2019, Seattle, USA.

\item \underline{Anke Lindner}, Brato Chakrabarti, Yanan Liu, Olivia du Roure and David Saintillan, \textit{The dynamics of flexible Brownian fibers in viscous flows} at  The Annual European Rheology Conference, Slovenia, April 8-11, 2019.

\item \underline{Brato Chakrabarti} and David Saintillan, \textit{Spontaneous oscillations and hydrodynamics of active micro-filament} at the 71st Annual Meeting of the APS Division of Fluid Dynamics, November 2018, Atlanta, USA. 

\item Roberto Alonso Matilla, Brato Chakrabarti and \underline{David Saintillan}, \textit{Asymptotic transport and dispersion of active particles in periodic porous media} at the 71st Annual Meeting of the APS Division of Fluid Dynamics, November 2018, Atlanta, USA. 

\item Brato Chakrabarti, \underline{Yanan Liu}, David Saintillan, Anke Lindner and Olivia du Roure, \textit{The dynamics of flexible and Brownian filaments in viscous flows} at the 71st Annual Meeting of the APS Division of Fluid Dynamics, November 2018, Atlanta, USA. 

\item \underline{Brato Chakrabarti}, Yanan Liu, David Saintillan, Anke Lindner and Olivia du Roure, \textit{Buckling and migration of semi-flexible filaments} at the 70th Annual Meeting of the APS Division of Fluid Dynamics, November 2017,
Denver,USA. 

\item \underline{David Saintillan} and Brato Chakrabarti, \textit{Shear dispersion in peristaltic pumping} at the 70th Annual Meeting of the APS Division of Fluid Dynamics, November 2017,
Denver,USA. 

\item \underline{James Hanna} and Brato Chakrabarti, \textit{Catenaries in viscous fluid}. $24^{th}$ ICTAM, Montreal, August 2016.

\item \underline{Brato Chakrabarti} and David Saintillan. \textit{Drift, Mixing and Diffusivity in 
	Stokes Flow}. Presented at the Southern California (SoCal) Fluids X, April 2016, UC Irvine, California, USA.

\item Brato Chakrabarti and \underline{James Hanna}. \textit{Catenaries in viscous fluid}. At the 68th Annual Meeting of the APS Division of Fluid Dynamics, November 2015,
Boston, USA. 

\item \underline{Brato Chakrabarti} and James Hanna. \textit{Catenaries in Drag}. Presented at the 67th Annual Meeting of the APS Division of Fluid Dynamics, November 2014,
San Francisco, USA. 
	
\end{enumerate}

\vspace*{-2mm}
\noindent\rule{\textwidth}{0.6pt}
\vspace*{-7mm}
\section{\color{Mahogany}{\large{INVITED TALKS}}}


\begin{enumerate}
	\vspace*{5mm}
	\item `Active caarpet model for intracellular flows', CompFlu, Indian Institute of Technology, Hyderabad, 2024.
	\item `From one to many: two problems in fluid-structure Interactions at low Reynolds number', LadHyX, Ecole Polytechnique, France, 2024. 
	\item `Problems and puzzles in intracellular flows', PMMH-ESPCI, Paris, France, 2024.
	\item `Self-organized intracellular flows: coarse-grained theory and the role of geometry', Symposium on Nonequilibrium and Active Matter Physics Meeting, Indian Institute of Science, 2024.
	\item `Self-organized intracellular flows: coarse-grained theory and the role of geometry', Symposium on Nonequilibrium and Active Matter Physics Meeting, Indian Institute of Science, 2024.
	\item `Self-organized intracellular flows: computational methods and coarse-grained theory', International Workshops on Advances in Computational Mechanics - IV, Kitakyushu, Japan, 2024.
	\item `Cytoplasmic streaming by active carpets', 9th Indian Statistical Physics Community Meeting, ICTS-TIFR, 2024.
	\item `Cytoplasmic streaming by active carpets', Mechanical Science Young Investigator Meeting (MSYIM), IIT Kanpur, 2024.
	\item `The waves within us: hydrodynamics of passive and active filaments', Indian Association for the Cultivation of Science, Kolkata, India, 2024.
	\item `The waves within us: hydrodynamics of passive and active filaments', University of California, Riverside, 2023.
	\item `Quantized metachronal waves in arrays of cilia', BPPB seminar (online), 2023.
	\item `Beat, sync, and wave: nonlinear dynamics of flagella and cilia', Department of Mechanical Engineering, IIT Bombay, 2023.
	\item `The waves within us: hydrodynamics of passive and active filaments', Jawaharlal Nehru Centre for Advanced Scientific Research (JNCASR), Bengaluru, 2023.
	\item `The waves within us: nonlinear dynamics of passive and active filaments', Tata Institute of Fundamental Research, Hyderabad, 2023.
	\item `A continuum theory for cytoplasmic streaming in the \textit{Drosophila} oocyte', International Center for Theoretical Sciences (ICTS), Bengaluru, 2022. 
	\item `Beat, sync, and wave: nonlinear dynamics of cilia and flagella', Colloquium, International Center for Theoretical Sciences (ICTS), Bengaluru, 2022. 
	\item `Problems on nonlinear dynamics of filaments in viscous fluids', Department of Applied Mechanics, Indian Institute of Technology, Madras, 2022.
	\item `From buckling to streaming: problems on fluid-structure interaction in viscous flows', Department of Mathematics, Princeton University, Analysis of Fluids Seminar, 2022.
	\item `The waves within us: problems on dynamics of passive and active filaments', International Center for Theoretical Sciences (ICTS), Bengaluru, 2022.
	\item `Problems on viscous dynamics of passive and active filaments: from one to many', Raman Research Institute (RRI), Bengaluru, 2022.
	\item `The waves within us: from single cilium to the formation of metachronal waves', Institute of Mathematical Sciences (IMSc), Madras, 2022.
	\item `The waves within us', Simons Foundation Lecture Series, Flatiron Institute, 2022.
	\item `A multiscale biophysical model gives quantized metachronal waves in a lattice of cilia', Frontiers in Applied \& Computational Mathematics, New Jersey Institute of Technology, 2022.
	\item `Hydrodynamics of Active Matter', Jadavpur University,  2021.
	
	\item  `Metachronal waves in ciliary arrays', Brown Bag Seminar, Center for Computational Biology, Flatiron Institute, 2020.
	
	\item  `Helical buckling of actin filaments in compressional flow', Biophysical Modeling group, Center for Computational Biology, Flatiron Institute, 2019.
	
	\item `Viscous dynamics of active and passive microfilaments',  Department of Physics, University of California, Santa Barbara, 2019.
	
	\item `Spontaneous oscillations and hydrodynamic synchronization of active filaments', ESPCI, Paris, France 2019. 
\end{enumerate}

\vspace*{-2mm}

\noindent\rule{\textwidth}{0.6pt}
\vspace*{-10mm}
\section{\color{Mahogany}{\large{OUTREACH}}}
\vspace*{6mm}
\begin{enumerate}
	\item \href{https://www.icts.res.in/lectures/sc-2024}{\textbf{ICTS summer course, 2024:}} Dynamics of biological systems (together with Prof. Akshit Goyal)
	
	\item \href{https://www.ncbs.res.in/events/physics-of-life-2024-9th-annual-monsoon-school}{\textbf{Physics of Life, NCBS monsoon school, 2024:}} Biological fluid flows and active matter
	
	\item \href{https://www.icts.res.in/outreach/other-events/BB2024}{\textbf{Beyond Boundaries: A Day of Interdisciplinary Exploration}}, ICTS, 2024
\end{enumerate}


%\vspace*{-2mm}
%\noindent\rule{\textwidth}{0.6pt}
%\vspace*{-10mm}
%\section{\color{Mahogany}{\large{STUDENTS MENTORED}}}
%\begin{multicols}{2}
%	\begin{itemize}
%		\item Arnab Paul (summer 2024)
%		\item Naveen Kumar D (summer 2024)
%		\item Anjali Kundalpady (Fall 2024)
%		\item Seema Chahal (Fall 2024)
%		\item Akash Sarkar (Fall 2024)
%		\item Sidarth S (LTVSP, 2024)
%	\end{itemize}
%\end{multicols}

\vspace*{-2mm}
\noindent\rule{\textwidth}{0.6pt}
\vspace*{-10mm}
\section{\color{Mahogany}{\large{AWARDS AND HONORS}}}
\vspace*{6mm}
\begin{enumerate}
	\item \textbf{Scientific High-Level Visiting Fellowships} from the French Institute of India, 2024.
	
	\item \textbf{Early Career Researcher} awarded by the journal \textit{Physics of Fluids}, 2020.
	
	\item \textbf{Powell Fellow, UCSD} by Jacobs school of Engineering, 2015.
	
	
	\item \textbf{Awarded Gold Medal} for best performance in Fluid Mechanics in Bachelor of Engineering (Mechanical Engineering, Jadavpur University), 2013.
	
	\item \textbf{National Merit Scholarship} for performance in school leaving examination, 2009.
\end{enumerate}

\vspace*{-5mm}
\noindent\rule{\textwidth}{0.6pt}
\vspace*{-10mm}
\section{\color{Mahogany}{\large{REVIEWER OF ARCHIVED JOURNALS}}}
\vspace*{3mm}


%\subsubsection*{{Reviewer for archived journals}}
\begin{multicols}{2}
	\begin{enumerate}
		\item Journal of Fluid Mechanics
		\item Physical Review Letters
		\item Physical Review Fluids
		\item Physical Review E
		\item Soft Matter
		\item Journal of Computational Physics
		\item Physica D
		\item New Journal of Physics
		\item Journal of Mathematical Fluid Mechanics
		\item Proceedings of the Royal Society A
		\item Proceedings of the National Academy of Science
		\item Nature Communications
	\end{enumerate}
\end{multicols}

\vspace*{-8mm}
\noindent\rule{\textwidth}{0.6pt}
\vspace*{-10mm}
\section{\color{Mahogany}{\large{TEACHING EXPERIENCE}}}
\paragraph{ICTS-TIFR}
\begin{itemize}
		\vspace*{2mm}
		\item Fall 2024: Fluid dynamics and elasticity
		\item Spring 2025: Biological fluid mechanics and active suspensions
\end{itemize} 

\paragraph{Virginia Tech} 
\begin{itemize}
	\vspace*{2mm}
	\item Fall 2013: Teaching Assistant, Statics  (ESM 2104)
	\item Spring 2014: Teaching Assistant, Dynamics (ESM 2204)
	\item Fall 2014: Teaching Assistant, Anaytical mechanics (ESM 3214)
	\item Spring 2015: Teaching Assistant, Vibrations (ESM 3134)
\end{itemize}

\vspace*{-2mm}
\paragraph{UCSD} 
\begin{itemize}
	\vspace*{2mm}
	\item Winter 2017: Teaching Assistant, Fluid mechanics (MAE 210 A)
	\item Fall   2018: Teaching Assistant, Introduction to mathematical physics (MAE 105).
	\item Spring 2019: Teaching Assistant, Hydrodynamic stability (MAE 210 C)
\end{itemize}
%%----------------------------------------------------------------------------------------
%\vspace*{-2mm}
%\noindent\rule{\textwidth}{0.6pt}
%\vspace*{-10mm}
%\section{\color{Mahogany}{\large{REFERENCES}} }
%
%\vspace*{4mm}
%
%\begin{multicols}{2}
%	\begin{enumerate}		
%		\item Prof. David Saintillan\\
%		Professor\\
%		Department of Mechanical and Aerospace Engineering \\
%		University of California, San Diego \\
%		E-mail: dsaintillan@eng.ucsd.edu  \\ 
%		Web: \url{http://stokeslet.ucsd.edu/} 
%		
%		\item Prof. Michael J. Shelley\\
%		Professor of Applied Mathematics\\
%		The Courant Institute of Mathematical Sciences   \\
%		Director, Center for Computational Biology \\ 
%		Flatiron Institute, Simons Foundation\\
%		E-mail: mshelley@simonsfoundation.org  \\ 
%		Web: \url{https://math.nyu.edu/faculty/shelley/} 
%		
%		\item Prof. Anke Lindner \\
%		Professor \\
%		Department of Physics, University Paris Diderot \\
%		E-mail: anke.lindner@espci.fr   \\
%		Web: \url{https://blog.espci.fr/alindner/} \\ 
%		
%	
%		\item Prof. Padmini Rangamani\\
%		Professor\\
%		Department of Mechanical and Aerospace Engineering \\
%		University of California, San Diego\\
%		E-mail: prangamani@ucsd.edu \\
%		Web: {\small{\url{https://sites.google.com/eng.ucsd.edu/prangamani}} }
%		
%		\item Prof. Sebastian  F\"{u}rthauer  \\
%		Assistant Professor \\
%		Institute for Applied Physics \\
%		TU Wien, Austria \\
%		E-mail: fuerthauer@iap.tuwien.ac.at \\
%		Web: \url{https://sflab.netlify.app/} \\
%%		
%		\item Prof. Stefan Llewellyn Smith\\
%		Professor\\
%		Department of Mechanical and Aerospace Engineering \\
%		University of California, San Diego \\
%		E-mail: sllewellynsmith@ucsd.edu \\
%		Web: \url{https://sites.google.com/a/eng.ucsd.edu/sgls/} \\
%			
%		
%		
%	\end{enumerate}
%\end{multicols}

\end{resume} 
\end{document}